Cluster Detection from three-dimensional Lensing Mass Map

### 2021-01-06 doc/paper_ms_method_HSCY1/sparse_NFW_results.tex
change the introduction

We test the algorithm with different regularization parameters ($\lambda$) for
the preliminary lasso estimation, which are $3.5$, $4.0$, and $5.0$. The
corresponding regularization parameters for the final adaptive lasso
estimations are set to $\lambda_{\rm{ada}}=\lambda^{\tau+1}$.  Here, we note
that both the preliminary lasso estimation and the final adaptive lasso
estimation select the pixels with the signal-to-noise ratios (SNRs) greater
than $\lambda$ in each gradient descent iteration and estimate the density in
the selected pixels. While the final adaptive lasso estimation further enhances
the growth of the pixels with preliminary estimations greater than $\lambda$.

@@

We select peaks with values greater than an ad-hoc threshold as candidates of
galaxy clusters following \citet{HSC1-massMap-cluster}.  The threshold is set
to a few times the standard deviation of the noise peaks. We use different
detection thresholds ($1.5\sigma$ and $3.0\sigma$) to detect galaxy clusters
from the mass maps reconstructed with $\lambda=3.5,4.0,5.0$. The left and
middle columns of Figure \ref{fig_detFalsRateNFW} show the detection rates for
halos in the (mass, redshift) planes with detection thresholds set to
$1.5\sigma$ and $3.0\sigma$ of the noise peaks' distributions, respectively.
The right column of Figure \ref{fig_detFalsRateNFW} shows the corresponding
numbers of false detections per square degree as functions of detection
thresholds. The first, second, and third rows of Figure
\ref{fig_detFalsRateNFW} correspond to the $lambda=3.5,4.0,5.0$, respectively.

>>>>

We test the algorithm with different regularization parameters ($\lambda$) for
the preliminary lasso estimation, which are $3.5$, $4.0$, and $5.0$. The
corresponding regularization parameters for the final adaptive lasso
estimations are set to $\lambda_{\rm{ada}}=\lambda^{\tau+1}$.  Here, we note
that both the preliminary lasso estimation and the final adaptive lasso
estimation select the pixels with the SNRs greater than $\lambda$ in each
gradient descent iteration and estimate the density in the selected pixels.
While the final adaptive lasso estimation further enhances the growth of the
pixels with preliminary estimations greater than $\lambda$.

@@

With the intent to suppress false detections, we select peaks with values
greater than an ad-hoc threshold as candidates of galaxy clusters following
\citet{WL-massMap-clusDet-HSC-Miyazaki2018}.  The threshold is set to a few
times the standard deviation of the noise peaks. We use different detection
thresholds ($1.5\sigma$ and $3.0\sigma$) to detect galaxy clusters from the
mass maps reconstructed with $\lambda=3.5,4.0,5.0$. The left and middle columns
of Figure \ref{fig_detFalsRateNFW} show the detection rates for halos in the
(mass, redshift) planes with detection thresholds set to $1.5\sigma$ and
$3.0\sigma$ of the noise peaks' distributions, respectively.  The right column
of Figure \ref{fig_detFalsRateNFW} shows the corresponding numbers of false
detections per square degree as functions of detection thresholds. The first,
second, and third rows of Figure \ref{fig_detFalsRateNFW} correspond to the
$lambda=3.5,4.0,5.0$, respectively.
